Geometric variational problems

### 2020-11-16 NSF2020/Description/DataManagement.tex
yny data management

\subsection*{Types of data to be produced during the course of the
project}
{\bf PI Ryham}: The following summarizes the type of analytical data to
be produced: \todo[inline]{Rolf to fill in}

@@

\noindent {\bf PI Young}: The following summarizes the type of
numerical/theoretical data to be produced: i) Mathematica files for the
theoretical modeling work, ii) Matlab codes and data array structures,
and iii) binary data from numerical simulations of the vesicle
osmophoresis. The estimated size of all the data is approximately 200 GB
per year. \todo[inline]{Yuan to update. This is what was in the CBET
proposal}

>>>>

\subsection*{Types of data to be produced during the course of the
project}
{\bf PI Ryham}:
The following summarizes the type of numerical data to
be produced:
(i) Matlab codes for running simulations and
processing figures,
(ii) Gnuplot code for creating manuscript figures, 
(iii) C++ code for large-scale simulations, and 
(iv) and ASCII files of simulation outputs. The estimated size of these
data will be under 1 TB for the duration of the project.

@@

\noindent {\bf PI Young}: The following summarizes the type of
numerical/theoretical data to be produced: i) Mathematica files for the
theoretical modeling work, ii) Matlab codes and data array structures,
and iii) binary data from numerical simulations of the vesicle
osmophoresis. The estimated size of all the data is approximately 200 GB
per year. 
%\todo[inline]{Yuan to update. This is what was in the CBET proposal}
